Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-23 paper.tex
Removed the manual firstrow on random-unreal and column training plots
Added utility matrics of all condition pairs
Modified <ROC curve> to <accuracy graph>

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/original_matrix_CentOS5vsCentOS7.pdf}
  \caption{Difference matrix, PreFreesurfer pipeline, CentOS~5 vs CentOS~7.}
  \label{fig:pre-freesurfer-5-7}
\end{figure}

@@

Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the ROC curves of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the ROC curves of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

All the other random methods, RS and both RFNT approaches 
are performing a continues growth Figure~\ref{fig:simple-methods} represents
the ROC curves of all random methods with comparision to dummy
classifier over the increasement of the training ratio.. Although some considerable variation 
for both triangular approches have been observed (CentOS5 vs CentOS6) 
their constant rise leads us to the next phase of experiments which was 
adding up bias into the current ALS technique. 
The training set suffers from lacking the files which are almost generated towareds the end of pipeline.

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS6}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	 \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
  \caption{Utility matrix of CentOS5 vs CentOS7}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
	\includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
  \caption{Utility matrix of CentOS6 vs CentOS7}
  \label{fig:utility metrics}
  \end{subfigure}
\end{figure}

@@

Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the accuracy graph of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

All the other random methods, RS and both RFNT approaches 
are performing a continues growth Figure~\ref{fig:simple-methods} represents
the accuracy graph of all random methods with comparision to dummy
classifier over the increasement of the training ratio.. Although some considerable variation 
for both triangular approches have been observed (CentOS5 vs CentOS6) 
their constant rise leads us to the next phase of experiments which was 
adding up bias into the current ALS technique. 
The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
